---
title: "CaseStudy2_MSDS"
author: "Simerpreet Reddy"
date: "March 11, 2020"
output:
  html_document: default
  pdf_document: default
---
Executive Summary:
At DDS Anlytics we specialize in Talent Management. Using our cutting edge technology and Frito Lay's employee data, we have developed a Talent Management solution that can help Frito Lay to identify and then control Attrition, manage employee training, analytically define salary and assess any job role related trends.

Purpose:
The purpose of this document is to provide analytical insights into Frito Lay's employee attrition data and to also provide insights on job role related trends.
This document also provides the models to predict attrition and salary of employees. 

This makes a great tool for Talent Management. 

The presenation for this analysis can be watched at this youtube video link: https://www.youtube.com/watch?v=SBntBfO1AiM&feature=youtu.be 



Job Role trends and Top attrition factors
```{r, message=F, warning=F}
#Include necessary libraries
library(tidyverse)
library(ggplot2)
library(caret)
library(tidyr)
library(dplyr)
library(e1071)
library(class)
library(gridExtra)

#Read source file
CaseStudy2_raw_hist <- read.csv(file.choose(), header = TRUE, sep=',')

#nrow(CaseStudy2_raw_hist)
#head(CaseStudy2_raw_hist)

#Rename columns for readability
colnames(CaseStudy2_raw_hist) <- c("ID",	"Age",	"Attrition",	"BusinessTravel",	"DailyRate",	"Department",	"DistanceFromHome",	"Education",	"EducationField",	"EmployeeCount",	"EmployeeNumber",	"EnvironmentSatisfaction",	"Gender",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole",	"JobSatisfaction",	"MaritalStatus",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18",	"OverTime",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager")

#Attrition Analysis
#Plot the distribution of data by Attrition
att_cnt <- data.frame("Measure" = c("Yes","No"), 
                      "Counts"= c(nrow(CaseStudy2_raw_hist %>% filter(Attrition=='Yes')),nrow(CaseStudy2_raw_hist %>% filter(Attrition=='No'))                                  ))

p_Att<- ggplot(data=att_cnt,mapping=aes(x=Measure, y= Counts, fill=Measure)) + geom_bar(stat="identity") + 
  ggtitle("Distribution of data by Attrition") +
  geom_text(aes(label = Counts), nudge_y = -10, color = "black") + xlab("Attrition") + ylab("Number of employees")

p_Att

#Filter out the row with null values
CaseStudy2_raw_hist <- CaseStudy2_raw_hist %>% filter(ID!=870)
#summary(CaseStudy2_raw_hist)
#str(CaseStudy2_raw_hist)

#Cut the differemt continous variable into groups/categories to be able to build histograms
#summary(CaseStudy2_raw_hist$Age)
CaseStudy2_raw_hist$Age_Grp <- cut(CaseStudy2_raw_hist$Age, breaks = c(17,21,30,35,43,61), labels = c("18-21","21-30" ,"30-35", "35-43", "43-60"))

#CaseStudy2_raw_hist$Age_Grp_Cat <- cut(CaseStudy2_raw_hist$Age, breaks = c(17,21,30,35,43,61), labels = c(1,2 ,3, 4, 5))
#summarise(CaseStudy2_raw_hist$Age_Grp_Cat)

#summary(CaseStudy2_raw_hist$DistanceFromHome)
CaseStudy2_raw_hist$DistfrmHome <- cut(CaseStudy2_raw_hist$DistanceFromHome, breaks = c(0,2,7,10,14,20,30), labels = c("0-2","2-7" ,"7-10", "10-14", "14-20","20-30"))
#summary(CaseStudy2_raw_hist$DistfrmHome)

#summary(CaseStudy2_raw_hist$MonthlyIncome)
CaseStudy2_raw_hist$MonthlyIncome_f <- cut(CaseStudy2_raw_hist$MonthlyIncome, breaks = c(1080,2838,4950,8189,20000), labels = c("1080-2838","2838-4950" ,"4950-8189", "8189-20000"))
#summary(CaseStudy2_raw_hist$MonthlyIncome_f)

#summary(CaseStudy2_raw_hist$MonthlyRate)	
CaseStudy2_raw_hist$MonthlyRate_f <- cut(CaseStudy2_raw_hist$MonthlyRate, breaks = c(2093,8059,14074,20460,26998), labels = c("2093-8059","8059-14074" ,"14074-20460", "20460-26998"))
#summary(CaseStudy2_raw_hist$MonthlyRate_f)	

#summary(CaseStudy2_raw_hist$NumCompaniesWorked)
CaseStudy2_raw_hist$NumCompaniesWorked_f <- cut(CaseStudy2_raw_hist$NumCompaniesWorked, breaks = c(-1,0,2,4,10), labels = c("0","1-2" ,"3-4", "5-10"))
#summary(CaseStudy2_raw_hist$NumCompaniesWorked_f)

#summary(CaseStudy2_raw_hist$TotalWorkingYears)
CaseStudy2_raw_hist$TotalWorkingYears_f <- cut(CaseStudy2_raw_hist$TotalWorkingYears, breaks = c(-1,1,6,10,15,41), labels = c("0","1-6","6-10" ,"10-15", "15-41"))
#summary(CaseStudy2_raw_hist$TotalWorkingYears_f	)


#summary(CaseStudy2_raw_hist$TrainingTimesLastYear)
CaseStudy2_raw_hist$TrainingTimesLastYear_f <- cut(CaseStudy2_raw_hist$TrainingTimesLastYear, breaks = c(-1,1,2,3,6), labels = c("0-1","2","2-3" ,"3-7"))
#summary(CaseStudy2_raw_hist$TrainingTimesLastYear_f)
#select(CaseStudy2_raw_hist, TrainingTimesLastYear,TrainingTimesLastYear_f)

#summary(CaseStudy2_raw_hist$YearsAtCompany	)
CaseStudy2_raw_hist$YearsAtCompany_f <- cut(CaseStudy2_raw_hist$YearsAtCompany, breaks = c(-1,1,3,5,10,41), labels = c("0","1-3" ,"3-5", "5-10", "10-41"))
#summary(CaseStudy2_raw_hist$YearsAtCompany_f	)

#summary(CaseStudy2_raw_hist$YearsInCurrentRole	)
CaseStudy2_raw_hist$YearsInCurrentRole_f <- cut(CaseStudy2_raw_hist$YearsInCurrentRole, breaks = c(-1,2,3,7,19), labels = c("0-2" ,"2-3", "3-7", "7-19"))
#select(CaseStudy2_raw_hist, YearsInCurrentRole,YearsInCurrentRole_f)
#summary(CaseStudy2_raw_hist$YearsInCurrentRole_f)

#summary(CaseStudy2_raw_hist$YearsSinceLastPromotion)
CaseStudy2_raw_hist$YearsSinceLastPromotion_f <- cut(CaseStudy2_raw_hist$YearsSinceLastPromotion, breaks = c(-1,0,1,3,16), labels = c("0","1","2-3" ,"3-15"))
#summary(CaseStudy2_raw_hist$YearsSinceLastPromotion_f)
#select(CaseStudy2_raw_hist, YearsSinceLastPromotion,YearsSinceLastPromotion_f)

#summary(CaseStudy2_raw_hist$YearsWithCurrManager)
CaseStudy2_raw_hist$YearsWithCurrManager_f <- cut(CaseStudy2_raw_hist$YearsWithCurrManager, breaks = c(-1,1,3,7,18), labels = c("0-1","2-3" ,"3-7", "7-17"))
#summary(CaseStudy2_raw_hist$YearsWithCurrManager_f)

#Convert numberic columns into factors
CaseStudy2_raw_hist$JobInvolvement <- as.factor(CaseStudy2_raw_hist$JobInvolvement)
CaseStudy2_raw_hist$JobLevel <- as.factor(CaseStudy2_raw_hist$JobLevel)
CaseStudy2_raw_hist$EnvironmentSatisfaction <- as.factor(CaseStudy2_raw_hist$EnvironmentSatisfaction)
CaseStudy2_raw_hist$Education <- as.factor(CaseStudy2_raw_hist$Education)
CaseStudy2_raw_hist$EnvironmentSatisfaction<- as.factor(CaseStudy2_raw_hist$EnvironmentSatisfaction)
CaseStudy2_raw_hist$JobInvolvement<- as.factor(CaseStudy2_raw_hist$JobInvolvement)
#CaseStudy2_raw_hist$JobLevel<- as.factor(CaseStudy2_raw_hist$JobLevel)
CaseStudy2_raw_hist$JobSatisfaction<- as.factor(CaseStudy2_raw_hist$JobSatisfaction)
CaseStudy2_raw_hist$RelationshipSatisfaction<- as.factor(CaseStudy2_raw_hist$RelationshipSatisfaction)
CaseStudy2_raw_hist$StockOptionLevel<- as.factor(CaseStudy2_raw_hist$StockOptionLevel)
CaseStudy2_raw_hist$WorkLifeBalance<- as.factor(CaseStudy2_raw_hist$WorkLifeBalance)

#Filter out rows where Attrition=Yes
CaseStudy2_raw_hist_ATT_Y <- CaseStudy2_raw_hist %>% filter(CaseStudy2_raw_hist$Attrition=='Yes')

#Age_group_by <- group_by(CaseStudy2_raw_hist_ATT_Y,Age_Grp_Cat)
#Perc_Att <- summarise(Age_group_by, perc_att= 
#plot(CaseStudy2_raw_hist["Attrition","Age_Grp"])
#CaseStudy2_raw_hist %>% filter(is.na(Age_Grp))

#Plot different measures to see how much they contributed to attrition
p_Age_grp <- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= Age_Grp), position="dodge") + ggtitle("Attrition counts in each age group")
p_BusinessTravel <- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= BusinessTravel), position="dodge") + ggtitle("Attrition counts by BusinessTravel group")
p_Department<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= Department), position="dodge") + ggtitle("Attrition counts in each Department")
p_EducationField<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= EducationField), position="dodge") + ggtitle("Attrition counts in each EducationField")
p_Gender<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= Gender), position="dodge") + ggtitle("Attrition counts in each Gender")
p_JobRole<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= JobRole), position="dodge") + ggtitle("Attrition counts in each JobRole")
p_MaritalStatus<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= MaritalStatus), position="dodge") + ggtitle("Attrition counts in each MaritalStatus")
p_OverTime<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= OverTime), position="dodge") + ggtitle("Attrition counts in each OverTime") 
p_JobInvolvement<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= JobInvolvement), position="dodge") + ggtitle("Attrition counts in each JobInvolvement")
p_DistfrmHome <- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= DistfrmHome), position="dodge") + ggtitle("Attrition counts in each DistfrmHome category")
p_Education <- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= Education), position="dodge") + ggtitle("Attrition counts in each Education level")
p_EnvironmentSatisfaction <- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= EnvironmentSatisfaction), position="dodge") + ggtitle("Attrition counts in each EnvironmentSatisfaction level")
p_JobInvolvement<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= JobInvolvement), position="dodge") + ggtitle("Attrition counts in each JobInvolvement")
p_JobLevel<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= JobLevel), position="dodge") + ggtitle("Attrition counts in each JobLevel")
p_JobSatisfaction<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= JobSatisfaction), position="dodge") + ggtitle("Attrition counts in each JobSatisfaction")
p_RelationshipSatisfaction<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= RelationshipSatisfaction), position="dodge") + ggtitle("Attrition counts in each RelationshipSatisfaction level")
p_StockOptionLevel<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= StockOptionLevel), position="dodge") + ggtitle("Attrition counts in each StockOptionLevel")
p_WorkLifeBalance<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= WorkLifeBalance), position="dodge") + ggtitle("Attrition counts in each WorkLifeBalance")
p_MonthlyIncome_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= MonthlyIncome_f), position="dodge") + ggtitle("Attrition counts in each MonthlyIncome category")
p_MonthlyRate_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= MonthlyRate_f), position="dodge") + ggtitle("Attrition counts in each MonthlyRate category")
p_NumCompaniesWorked_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= NumCompaniesWorked_f), position="dodge") + ggtitle("Attrition counts in each NumCompaniesWorked category")
p_TotalWorkingYears_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= TotalWorkingYears_f), position="dodge") + ggtitle("Attrition counts in each TotalWorkingYears category")
p_TrainingTimesLastYear_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= TrainingTimesLastYear_f), position="dodge") + ggtitle("Attrition counts in each TrainingTimesLastYear category")
p_YearsAtCompany_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= YearsAtCompany_f), position="dodge") + ggtitle("Attrition counts in each YearsAtCompany category")
p_YearsInCurrentRole_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= YearsInCurrentRole_f), position="dodge") + ggtitle("Attrition counts in each YearsInCurrentRole category")
p_YearsSinceLastPromotion_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= YearsSinceLastPromotion_f), position="dodge") + ggtitle("Attrition counts in each YearsSinceLastPromotion category")
p_YearsWithCurrManager_f<- ggplot(data=CaseStudy2_raw_hist_ATT_Y) + geom_bar(mapping=aes(x=Attrition, fill= YearsWithCurrManager_f), position="dodge") + ggtitle("Attrition counts in each YearsWithCurrManager category")

#grid.arrange(p_Age_grp,p_BusinessTravel,p_Department,p_EducationField,p_Gender,p_JobRole,p_MaritalStatus,p_OverTime,p_JobInvolvement,ncol = 3, nrow=3)
#grid.arrange(p_DistfrmHome,p_Education,p_EnvironmentSatisfaction,p_JobInvolvement, p_JobLevel,p_JobSatisfaction,p_RelationshipSatisfaction,p_StockOptionLevel,p_WorkLifeBalance,ncol = 3, nrow=3)
#grid.arrange(p_MonthlyIncome_f,p_MonthlyRate_f,p_NumCompaniesWorked_f,p_TrainingTimesLastYear_f,p_YearsAtCompany_f,p_YearsInCurrentRole_f,p_YearsSinceLastPromotion_f,p_YearsWithCurrManager_f,ncol = 3, nrow=3)

grid.arrange(p_Age_grp,p_BusinessTravel,ncol = 2, nrow=1)
grid.arrange(p_Department,p_EducationField, ncol = 2, nrow=1)
grid.arrange(p_Gender,p_JobRole,ncol = 2, nrow=1)
grid.arrange(p_MaritalStatus,p_OverTime,ncol = 2, nrow=1)
grid.arrange(p_JobInvolvement,p_DistfrmHome,ncol = 2, nrow=1)
grid.arrange(p_Education,p_EnvironmentSatisfaction,ncol = 2, nrow=1)
grid.arrange(p_JobInvolvement, p_JobLevel,ncol = 2, nrow=1)
grid.arrange(p_JobSatisfaction,p_RelationshipSatisfaction, ncol = 2, nrow=1)
grid.arrange(p_StockOptionLevel,p_WorkLifeBalance,ncol = 2, nrow=1)
grid.arrange(p_MonthlyIncome_f,p_MonthlyRate_f,ncol = 2, nrow=1)
grid.arrange(p_NumCompaniesWorked_f,p_TrainingTimesLastYear_f,ncol = 2, nrow=1)
grid.arrange(p_YearsAtCompany_f,p_YearsInCurrentRole_f,ncol = 2, nrow=1)
grid.arrange(p_YearsSinceLastPromotion_f,p_YearsWithCurrManager_f,ncol = 2, nrow=1)

msg <- "We see that for a lot of measures, certain categories standout when seeing only the attirion data. \n Out of all the measures, the following measures made for more than 75 out of total 141 records where attrition=Yes.\n MaritalStatus=Single\n Dept=RnD \n Overtime=Yes\n WorkLifeBalance=3 \n Job_Level=1 \n Gender=Male \n YrsInCurrentRole=0-2 \n Business Travel=Travel Rarely \n StockOption=0 \n Let's study them all in detail"
strsplit(msg,"\n")

Total_Att <-nrow(CaseStudy2_raw_hist_ATT_Y)
Att_Y_BusinessTravel_Travel_Rarely <-   round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(BusinessTravel=='Travel_Rarely')))/Total_Att)*100,2)
Att_Y_Department_RnD <-  round( ((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(Department=='Research & Development')))/Total_Att)*100,2)
Att_Y_Gender_M  <-    round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(Gender=='Male')))/Total_Att)*100,2)
Att_Y_Overtime_Y <-   round( ((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(OverTime=='Yes')))/Total_Att)*100,2)
Att_Y_Marital_Status_S <-    round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(MaritalStatus=='Single')))/Total_Att)*100,2)
Att_Y_Job_Level_1 <-    round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(JobLevel=='1')))/Total_Att)*100,2)
Att_Y_Stock_Option_0 <-    round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(StockOptionLevel=='0')))/Total_Att)*100,2)
Att_Y_WrrkLB_3 <-    round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(WorkLifeBalance=='3')))/Total_Att)*100,2)
Att_Y_YearsInCurrentRole_0_2 <-round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(YearsInCurrentRole =="0" | YearsInCurrentRole =="1" | YearsInCurrentRole =="2"  )))/Total_Att)*100,2)
Att_Y_JobInvolvement_3 <-round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(JobInvolvement =="3" )))/Total_Att)*100,2)
Att_Y_p_MonthlyIncome_f_1080_2838 <-round(((nrow(CaseStudy2_raw_hist_ATT_Y %>% filter(MonthlyIncome_f =="1080-2838" | YearsInCurrentRole =="1" | YearsInCurrentRole =="2"  )))/Total_Att)*100,2)


Top_Att_Measures <- data.frame("Measure_Name" = c("BusinessTravel=Travel Rarely", "Department=RnD","Gender=Male","Overtime=Yes", "MaritalStatus=Single", "Job_Level=1", "StockOption=0",
                                                  "WorkLifeBalance=3","YearsInCurrentRole=0-2","JobInvolvement=3","MonthlyIncome=1080-2838" ), 
"Att_perc"= c(Att_Y_BusinessTravel_Travel_Rarely,Att_Y_Department_RnD,Att_Y_Gender_M,Att_Y_Overtime_Y,Att_Y_Marital_Status_S,
              Att_Y_Job_Level_1,Att_Y_Stock_Option_0,Att_Y_WrrkLB_3 ,Att_Y_YearsInCurrentRole_0_2,Att_Y_JobInvolvement_3,Att_Y_p_MonthlyIncome_f_1080_2838))


positions=c("JobInvolvement=3","MaritalStatus=Single","Department=RnD","Overtime=Yes","WorkLifeBalance=3","MonthlyIncome=1080-2838" ,"Job_Level=1","Gender=Male","YearsInCurrentRole=0-2","BusinessTravel=Travel Rarely","StockOption=0")
ggplot(data=Top_Att_Measures,mapping=aes(y=Att_perc, x= Measure_Name, fill=Measure_Name)) + geom_bar( stat='identity',show.legend = FALSE) +
    geom_text(aes(label = Att_perc), nudge_y = -3, color = "black") + scale_x_discrete(limits = positions) +
  ggtitle("Chart shows what percent of each factor contributed to total attrition") + 
  xlab("") +ylab("Percent of Total Attrition across the Org") +
  coord_flip() 


print("Conclusion: To control Attrition, we should start by focussing on employees who fall in following categories: 1) Stock Option Level=0, 2) Those who go rarely on a business travel 3) 0-2 years in their current role")




# 2 Attrition Analysis by Department
#Divide data by department
data_dept_Sales <- CaseStudy2_raw_hist %>% filter(Department=='Sales')
data_dept_HR <- CaseStudy2_raw_hist %>% filter(Department=='Human Resources')
data_dept_RnD <- CaseStudy2_raw_hist %>% filter(Department=='Research & Development')
#nrow(data_dept_Sales)
#nrow(data_dept_HR)
#nrow(data_dept_RnD)

#Calculate total attrition and attrition % in each department
#Calculate total attrition in the entire data set
Cnt_Att_Yes <- nrow(CaseStudy2_raw_hist %>% filter(Attrition=="Yes"))
Cnt_Total <-nrow(CaseStudy2_raw_hist)
Attrition_Perc <- round((Cnt_Att_Yes/Cnt_Total)*100,0)

Cnt_Att_Yes_Sales <- nrow(data_dept_Sales %>% filter(Attrition=="Yes"))
Cnt_Total_Sales <-nrow(data_dept_Sales)
Cnt_Total_Sales_Perc <- round((Cnt_Total_Sales/Cnt_Total)*100,0)
Attrition_Perc_Sales <- round((Cnt_Att_Yes_Sales/Cnt_Total_Sales)*100,0)
Attrition_Perc_Sales  #21.61
Overall_Attrition_Perc_Sales <- round((Cnt_Att_Yes_Sales/Cnt_Att_Yes)*100,0)

Cnt_Att_Yes_HR <- nrow(data_dept_HR %>% filter(Attrition=="Yes"))
Cnt_Total_HR <-nrow(data_dept_HR)
Cnt_Total_HR_Perc <- round((Cnt_Total_HR/Cnt_Total)*100,0)
Attrition_Perc_HR <- round((Cnt_Att_Yes_HR/Cnt_Total_HR)*100,0)
Attrition_Perc_HR  #17.14
Overall_Attrition_Perc_HR <- round((Cnt_Att_Yes_HR/Cnt_Att_Yes)*100,0)

Cnt_Att_Yes_RnD <- nrow(data_dept_RnD %>% filter(Attrition=="Yes"))
Cnt_Total_RnD <-nrow(data_dept_RnD)
Cnt_Total_RnD_Perc <- round((Cnt_Total_RnD/Cnt_Total)*100,0)
Attrition_Perc_RnD <- round((Cnt_Att_Yes_RnD/Cnt_Total_RnD)*100,0)
Attrition_Perc_RnD  #13.37
Overall_Attrition_Perc_RnD <- round((Cnt_Att_Yes_RnD/Cnt_Att_Yes)*100,0)


# Overall Attrition
OrgWide_Attrition <- data.frame( "Total_employees"= Cnt_Total,"Total_Attr"=Cnt_Att_Yes, "Attr_rate"= Attrition_Perc)
                                 
#Attrition % by dept
Attr_rate_by_dept <- data.frame( "Dept" = c("Sales","HR", "RnD", "OrgWide"),
                                 "Total_emp"= c(Cnt_Total_Sales,Cnt_Total_HR,Cnt_Total_RnD,Cnt_Total),
                                 "Total_emp_Perc"= c(Cnt_Total_Sales_Perc,Cnt_Total_HR_Perc,Cnt_Total_RnD_Perc,Cnt_Total),
                                 "Attr_num"=c(Cnt_Att_Yes_Sales, Cnt_Att_Yes_HR,Cnt_Att_Yes_RnD,Cnt_Att_Yes), 
                                 "Attr_rate_dept"= c( Attrition_Perc_Sales,Attrition_Perc_HR,Attrition_Perc_RnD,Attrition_Perc),
                                 "Overall_Att_Perc" = c(Overall_Attrition_Perc_Sales,Overall_Attrition_Perc_HR,Overall_Attrition_Perc_RnD,Attrition_Perc))

Attr_rate_by_dept
summary(Attr_rate_by_dept)


Attr_rate_by_dept_only <- Attr_rate_by_dept %>% filter(Dept!="OrgWide")

#Distribution of employees by department
#ggplot(data=Attr_rate_by_dept_only) + geom_histogram(mapping=aes(y=Total_emp_Perc, x= Dept, fill=Dept), stat="identity") + xlab("Department") + ylab("Attrition Rate") + ggtitle("Distribution of employees by department")

p1 <- ggplot(data=Attr_rate_by_dept_only, mapping=aes(y=Total_emp_Perc, x= Dept, fill=Dept)) + geom_bar(stat="identity",show.legend = FALSE)  + xlab("Department") +
  ylab("% of employees") + ggtitle("Distribution of employees by department") +
  geom_text(aes(label = Total_emp_Perc), nudge_y = -1, color = "black")
p1
print("RnD department has the most number of employess")

#Orgwide attrition rate comparision BY department
p2 <- ggplot(data=Attr_rate_by_dept_only,mapping=aes(y=Overall_Att_Perc, x= Dept, fill=Dept)) + geom_bar(stat="identity",show.legend = FALSE) + xlab("Department") +
  ylab("Attrition Rate") + ggtitle("Orgwide attrition rate comparision BY department") +
  geom_text(aes(label = Overall_Att_Perc), nudge_y = -1, color = "black")
p2
print("Orgwide attrition rate is highest in RnD department")
Attr_rate_by_dept

#Attrition rate comparision WITHIN each department
p3<- ggplot(data=Attr_rate_by_dept_only,mapping=aes(y=Attr_rate_dept, x= Dept, fill=Dept)) + geom_histogram(stat="identity")  + xlab("Department") +
  ylab("Attrition Rate") + ggtitle("Attrition rate comparision WITHIN each department") +
  geom_text(aes(label = Attr_rate_dept), nudge_y = -1, color = "black")
p3
print("Attrition is highest in Sales department, let's dive deep into this")

grid.arrange(p1,p2, p3, ncol = 3)

print("RnD department has the most number of employess, and has the most the number of attritions as well.But comparing the attrition within departments, we see that the Sales department had the highest attrition rate")



#Attrition analysis in Sales department
Sales_att <- CaseStudy2_raw_hist %>% filter(Department=='Sales' & Attrition=='Yes')
#nrow(Sales_att)
#Plot different measures to see how much they contributed to attrition
Sales_p_Age_grp <- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= Age_Grp), position="dodge") + ggtitle("Attrition by age")
Sales_p_BusinessTravel <- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= BusinessTravel), position="dodge") + ggtitle("Attrition by BusinessTravel")
Sales_p_EducationField<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= EducationField), position="dodge") + ggtitle("Attrition by EducationField")
Sales_p_Gender<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= Gender), position="dodge") + ggtitle("Attrition by Gender")
Sales_p_JobRole<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= JobRole), position="dodge") + ggtitle("Attrition by JobRole")
Sales_p_MaritalStatus<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= MaritalStatus), position="dodge") + ggtitle("Attrition by MaritalStatus")
Sales_p_OverTime<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= OverTime), position="dodge") + ggtitle("Attrition by OverTime") 
Sales_p_JobInvolvement<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= JobInvolvement), position="dodge") + ggtitle("Attrition by JobInvolvement")
Sales_p_DistfrmHome <- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= DistfrmHome), position="dodge") + ggtitle("Attrition by age DistancefrmHome")
Sales_p_Education <- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= Education), position="dodge") + ggtitle("Attrition by Education level")
Sales_p_EnvironmentSatisfaction <- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= EnvironmentSatisfaction), position="dodge") + ggtitle("Attrition by EnvironmentSatisfaction")
Sales_p_JobInvolvement<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= JobInvolvement), position="dodge") + ggtitle("Attrition by obInvolvement")
Sales_p_JobLevel<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= JobLevel), position="dodge") + ggtitle("Attrition counts by obLevel")
Sales_p_JobSatisfaction<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= JobSatisfaction), position="dodge") + ggtitle("Attrition by JobSatisfaction")
Sales_p_RelationshipSatisfaction<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= RelationshipSatisfaction), position="dodge") + ggtitle("Attrition by elationshipSatisfaction")
Sales_p_StockOptionLevel<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= StockOptionLevel), position="dodge") + ggtitle("Attrition by StockOptionLevel")
Sales_p_WorkLifeBalance<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= WorkLifeBalance), position="dodge") + ggtitle("Attrition by WorkLifeBalance")
Sales_p_MonthlyIncome_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= MonthlyIncome_f), position="dodge") + ggtitle("Attrition by MonthlyIncome")
Sales_p_MonthlyRate_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= MonthlyRate_f), position="dodge") + ggtitle("Attrition by MonthlyRate")
Sales_p_NumCompaniesWorked_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= NumCompaniesWorked_f), position="dodge") + ggtitle("Attrition by NumCompaniesWorked")
Sales_p_TotalWorkingYears_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= TotalWorkingYears_f), position="dodge") + ggtitle("Attrition by TotalWorkingYears")
Sales_p_TrainingTimesLastYear_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= TrainingTimesLastYear_f), position="dodge") + ggtitle("Attrition by TrainingTimesLastYear")
Sales_p_YearsAtCompany_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= YearsAtCompany_f), position="dodge") + ggtitle("Attrition by YearsAtCompany")
Sales_p_YearsInCurrentRole_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= YearsInCurrentRole_f), position="dodge") + ggtitle("Attrition by YearsInCurrentRole")
Sales_p_YearsSinceLastPromotion_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= YearsSinceLastPromotion_f), position="dodge") + ggtitle("Attrition by YearsSinceLastPromotion")
Sales_p_YearsWithCurrManager_f<- ggplot(data=Sales_att) + geom_bar(mapping=aes(x=Attrition, fill= YearsWithCurrManager_f), position="dodge") + ggtitle("Attrition by YearsWithCurrManager")

grid.arrange(Sales_p_Age_grp,Sales_p_BusinessTravel,Sales_p_Education,Sales_p_EducationField,Sales_p_Gender,Sales_p_JobRole,Sales_p_MaritalStatus,Sales_p_OverTime,Sales_p_JobInvolvement,ncol = 3, nrow=3)
grid.arrange(Sales_p_DistfrmHome,Sales_p_EnvironmentSatisfaction,Sales_p_JobInvolvement, Sales_p_JobLevel,Sales_p_JobSatisfaction,Sales_p_RelationshipSatisfaction,Sales_p_StockOptionLevel,Sales_p_WorkLifeBalance,ncol = 3, nrow=3)
grid.arrange(Sales_p_MonthlyIncome_f,Sales_p_MonthlyRate_f,Sales_p_NumCompaniesWorked_f,Sales_p_TrainingTimesLastYear_f,Sales_p_YearsAtCompany_f,Sales_p_YearsInCurrentRole_f,Sales_p_YearsSinceLastPromotion_f,Sales_p_YearsWithCurrManager_f,ncol = 3, nrow=3)





#3 Job Role specific trends
Job_Lvl_p_Age_grp <- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= Age_Grp),show.legend = FALSE) + ggtitle("Age")   + ylab("Number of employess")
Job_Lvl_p_Gender<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= Gender),show.legend = FALSE) + ggtitle("Gender")   + ylab("")
Job_Lvl_p_MaritalStatus<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= MaritalStatus)) + ggtitle("MaritalStatus")    + ylab("")
Job_Lvl_p_OverTime<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= OverTime),show.legend = FALSE) + ggtitle("OverTime")    + ylab("Number of employess")
Job_Lvl_p_JobInvolvement<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= JobInvolvement),show.legend = FALSE) + ggtitle("JobInvolvement")  + ylab("")
Job_Lvl_p_Education <- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= Education),show.legend = FALSE) + ggtitle("Education level")  + ylab("")

Job_Lvl_p_EnvironmentSatisfaction <- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= EnvironmentSatisfaction),show.legend = FALSE) + ggtitle("EnvironmentSatisfaction")   + ylab("Number of employess")
#Job_Lvl_p_JobInvolvement<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= JobInvolvement),show.legend = FALSE) + ggtitle("JobInvolvement")   + ylab("")
Job_Lvl_p_JobSatisfaction<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= JobSatisfaction)) + ggtitle("JobSatisfaction")   + ylab("")
Job_Lvl_p_RelationshipSatisfaction<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= RelationshipSatisfaction),show.legend = FALSE) + ggtitle("RelationshipSatisfaction")    + ylab("Number of employess")
Job_Lvl_p_StockOptionLevel<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= StockOptionLevel),show.legend = FALSE) + ggtitle("StockOptionLevel")   + ylab("")
Job_Lvl_p_WorkLifeBalance<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x = WorkLifeBalance),show.legend = FALSE) + ggtitle("WorkLifeBalance")   + ylab("")

Job_Lvl_p_MonthlyIncome_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= MonthlyIncome_f),show.legend = FALSE) + ggtitle("MonthlyIncome")    + ylab("Number of employess")
Job_Lvl_p_MonthlyRate_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= MonthlyRate_f),show.legend = FALSE) + ggtitle("MonthlyRate")    + ylab("")
Job_Lvl_p_NumCompaniesWorked_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= NumCompaniesWorked_f)) + ggtitle("NumCompaniesWorked")    + ylab("")
Job_Lvl_p_TotalWorkingYears_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= TotalWorkingYears_f),show.legend = FALSE) + ggtitle("TotalWorkingYears")    + ylab("Number of employess")
Job_Lvl_p_TrainingTimesLastYear_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= TrainingTimesLastYear_f),show.legend = FALSE) + ggtitle("TrainingTimesLastYear")  + ylab("")
Job_Lvl_p_YearsAtCompany_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= YearsAtCompany_f),show.legend = FALSE) + ggtitle("YearsAtCompany")  + ylab("")

Job_Lvl_p_YearsInCurrentRole_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= YearsInCurrentRole_f),show.legend = FALSE) + ggtitle("YearsInCurrentRole")  + ylab("Number of employess")
Job_Lvl_p_YearsSinceLastPromotion_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= YearsSinceLastPromotion_f)) + ggtitle("YearsSinceLastPromotion")  + ylab("")
Job_Lvl_p_YearsWithCurrManager_f<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= YearsWithCurrManager_f),show.legend = FALSE) + ggtitle("YearsWithCurrManager")   + ylab("")
Job_Lvl_p_DistfrmHome <- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= DistfrmHome),show.legend = FALSE) + ggtitle("DistanceFromHome") + ylab("Number of employess") +xlab("DistanceFromHome")

Job_Lvl_p_BusinessTravel <- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= BusinessTravel),show.legend = FALSE) + ggtitle("BusinessTravel") + coord_flip() + xlab("") + ylab("Number of employess")
Job_Lvl_p_Department<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= Department),show.legend = FALSE) + ggtitle("Department")+ coord_flip()  + xlab("") + ylab("Number of employess")
Job_Lvl_p_EducationField<- ggplot(data= CaseStudy2_raw_hist) + geom_bar(mapping=aes(fill=JobRole, x= EducationField)) + ggtitle("EducationField")  + coord_flip() + xlab("") + ylab("Number of employess")


grid.arrange(Job_Lvl_p_BusinessTravel,Job_Lvl_p_Department,Job_Lvl_p_EducationField,ncol = 3, nrow=1)
grid.arrange(Job_Lvl_p_Age_grp,Job_Lvl_p_Gender,Job_Lvl_p_MaritalStatus,Job_Lvl_p_OverTime,Job_Lvl_p_JobInvolvement,Job_Lvl_p_Education,ncol = 3, nrow=2)
grid.arrange(Job_Lvl_p_EnvironmentSatisfaction,Job_Lvl_p_JobInvolvement,Job_Lvl_p_JobSatisfaction,Job_Lvl_p_RelationshipSatisfaction,Job_Lvl_p_StockOptionLevel,Job_Lvl_p_WorkLifeBalance,ncol = 3, nrow=2)
grid.arrange(Job_Lvl_p_MonthlyIncome_f,Job_Lvl_p_MonthlyRate_f,Job_Lvl_p_NumCompaniesWorked_f,Job_Lvl_p_TotalWorkingYears_f,Job_Lvl_p_TrainingTimesLastYear_f,Job_Lvl_p_YearsAtCompany_f,ncol = 3, nrow=2)
grid.arrange(Job_Lvl_p_YearsInCurrentRole_f,Job_Lvl_p_YearsSinceLastPromotion_f,Job_Lvl_p_YearsWithCurrManager_f,Job_Lvl_p_DistfrmHome,ncol = 2, nrow=2)

```
 


#Classification and Regression Model
```{r, message=F, warning=F}
#Include encessary libraries
library(tidyverse)
library(ggplot2)
library(caret)
library(tidyr)
library(dplyr)
library(e1071)
library(class)

#Read Source file
CaseStudy2_raw <- read.csv(file.choose(), header = TRUE, sep=',')


#Read No Attritions File
CaseStudy2_Comp_set<- read.csv(file.choose(), header = TRUE, sep=',')


#Read No Salary file
CaseStudy2_Comp_Sal_set<- read.csv(file.choose(), header = TRUE, sep=',')

#colnames(CaseStudy2_raw)
#nrow(CaseStudy2_raw)
#head(CaseStudy2_raw)
colnames(CaseStudy2_raw) <- c("ID",	"Age",	"Attrition",	"BusinessTravel",	"DailyRate",	"Department",	"DistanceFromHome",	"Education",	"EducationField",	"EmployeeCount",	"EmployeeNumber",	"EnvironmentSatisfaction",	"Gender",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole",	"JobSatisfaction",	"MaritalStatus",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18",	"OverTime",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager")
#Rename for test file
#colnames(CaseStudy2_raw) <- c("ID",	"Age","BusinessTravel",	"DailyRate",	"Department",	"DistanceFromHome",	"Education",	"EducationField",	"EmployeeCount",	"EmployeeNumber",	"EnvironmentSatisfaction",	"Gender",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole",	"JobSatisfaction",	"MaritalStatus",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18",	"OverTime",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager")


CaseStudy2_raw <- CaseStudy2_raw %>% filter(ID!=870)
#summary(CaseStudy2_raw)

#Final_Model_Results <- data.frame( "Test_Type" = character(), "Accuracy_knn" = double(),"Accuracy_NB" = double(), 
#                                   "Specificity_knn" = double(), "Specificity_NB" = double(), 
#                                   "Sensitivity_knn" = double(), "Sensitivity_NB" = double(), "DAta_Set_Name"=character())

#Replace char values with numerical values - Business Travel(1-3), Gender(1,2), Marital Status -(1-3), OverTime (1,2), JobRole,EducationField,Department
CaseStudy2_raw$BusinessTravel_N <- ifelse(str_detect(CaseStudy2_raw$BusinessTravel,'Non-Travel'),1, ifelse(str_detect(CaseStudy2_raw$BusinessTravel,'Travel_Rarely'),2,ifelse(str_detect(CaseStudy2_raw$BusinessTravel,'Travel_Frequently'),3,4)))
CaseStudy2_raw$Gender_N <-ifelse(str_detect(CaseStudy2_raw$Gender,"^Male"),1, ifelse(str_detect(CaseStudy2_raw$Gender,"^Female"),2,3))
CaseStudy2_raw$Over18_N <-ifelse(str_detect(CaseStudy2_raw$Over18,"Y"),1, 2)
CaseStudy2_raw$MaritalStatus_N <- ifelse(str_detect(CaseStudy2_raw$MaritalStatus,'Single'),1, ifelse(str_detect(CaseStudy2_raw$MaritalStatus,'Married'),2,ifelse(str_detect(CaseStudy2_raw$MaritalStatus,'Divorced'),3,4)))
CaseStudy2_raw$OverTime_N <-ifelse(str_detect(CaseStudy2_raw$OverTime,"No"),1, ifelse(str_detect(CaseStudy2_raw$OverTime,"Yes"),2,3))
CaseStudy2_raw$Department_N <- ifelse(str_detect(CaseStudy2_raw$Department,"Human Resources"),1, ifelse(str_detect(CaseStudy2_raw$Department,"Research & Development"),2,3))
CaseStudy2_raw$EducationField_N <- ifelse(str_detect(CaseStudy2_raw$Department,"Human Resources"),1,ifelse(str_detect(CaseStudy2_raw$Department,"Life Sciences"),2,
                                                                                                           ifelse(str_detect(CaseStudy2_raw$Department,"Marketing"),3, 
                                                                                                                  ifelse(str_detect(CaseStudy2_raw$Department, "Medical"),4,  
                                                                                                                         ifelse(str_detect(CaseStudy2_raw$Department,"Other"),5, 6)))))     

CaseStudy2_raw$JobRole_N <- ifelse(str_detect(CaseStudy2_raw$JobRole,"Sales Executive"),1,ifelse(str_detect(CaseStudy2_raw$Department,"Research Scientist"),2,
                                                                                                           ifelse(str_detect(CaseStudy2_raw$Department,"Laboratory Technician"),3, 
                                                                                                                  ifelse(str_detect(CaseStudy2_raw$Department, "Manufacturing Director"),4,  
                                                                                                                         ifelse(str_detect(CaseStudy2_raw$Department,"Healthcare Representative"),5, 
                                                                                                                                ifelse(str_detect(CaseStudy2_raw$Department,"Sales Representative"),6, 
                                                                                                                                7)))))   )  

#CaseStudy2_raw %>% select(JobRole_N,JobRole)
#summary(CaseStudy2_raw)

#Exclude employee number and employee cnt from the data
#CaseStudy2_N <- CaseStudy2_raw %>% select("ID",	"Attrition","Age","BusinessTravel_N",	"DailyRate",	"Department_N",	"DistanceFromHome",	"Education",	"EducationField_N",	"EmployeeCount","EnvironmentSatisfaction",	"Gender_N",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole_N",	"JobSatisfaction",	"MaritalStatus_N",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18_N",	"OverTime_N",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager")

CaseStudy2_N <- CaseStudy2_raw %>% select("ID",	"Attrition","Age","BusinessTravel_N",	"DailyRate",	"Department_N",	"DistanceFromHome",	"Education",	"EducationField_N","EnvironmentSatisfaction",	"Gender_N",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole_N",	"JobSatisfaction",	"MaritalStatus_N",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18_N",	"OverTime_N",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager")


#Plotting the data
#plot(CaseStudy2_N)


##Base_Data <- CaseStudy2_N #data_Grp_1 # OR data_Grp_1 or data_Grp_2_Nmbr
#Base_Data_Name <- "CaseStudy2_N" # or Data_Group_2
#Number_of_Cols <- ncol(Base_Data)
#Start Modelling the data  
#1 Normalize the data
#normalize <- function(x) {return ((x - min(x)) / (max(x) - min(x))) }
#Base_Data_n <- as.data.frame(lapply(Asnumber_Base_Data[,3:Number_of_Cols], normalize))
#head(Base_Data_n)
#Base_Data_knn <- cbind(Base_Data[1],Base_Data[2],Base_Data_n)
#head(Base_Data_knn)

#Normalize the data using zscore
library(jmotif)
#Asnumber <- function(x) {return (as.numeric(x)) }
#Asnumber_Base_Data <- as.data.frame(lapply(Base_Data[,3:Number_of_Cols], Asnumber))
#Number_of_Cols <- ncol(Asnumber_Base_Data)
#Base_Data_Z <- znorm(Asnumber_Base_Data[,3]):Number_of_Cols]))
#normalize(Base_Data, method="Z-score")
#summary(Asnumber_Base_Data)

#CaseStudy2_N 
Number_of_Cols_1 <- ncol(CaseStudy2_N)
Asnumber <- function(x) {return (as.numeric(x)) } # function convert measures to numberic
CaseStudy2_N_nmbr <- as.data.frame(lapply(CaseStudy2_N[,3:Number_of_Cols_1], Asnumber))
znorm_f <-function(x) {return (znorm(x)) } # function to Z-norm the data
Number_of_Cols_2 <- ncol(CaseStudy2_N_nmbr)
znorm_CaseStudy2_N_nmbr <- as.data.frame(lapply(CaseStudy2_N_nmbr[,1:Number_of_Cols_2], znorm_f))
CaseStudy2_N_Z <- cbind(CaseStudy2_N[1],CaseStudy2_N[2],znorm_CaseStudy2_N_nmbr) #combine z-norm data with ID and Attrition values
#head(CaseStudy2_N_Z)
Base_Data <- CaseStudy2_N_Z
Number_of_Cols <- ncol(CaseStudy2_N_Z)

#2 Finding K value with highest accuracy
Acc= matrix(nrow=100, ncol=100)
for (seed in 1:100)
{
  
  #seed=4
  set.seed(seed)
  trainIndices = sample(seq(1:nrow(Base_Data)),round(.7*nrow(Base_Data)))
  train_data = Base_Data[trainIndices,]
  test_data = Base_Data[-trainIndices,] 
  #nrow(train_CaseStudy2_raw) #609
  #nrow(test_CaseStudy2_raw)  #261
  ncol(train_data)
  
  #For loop to run KNN model for k=1-100  
  for( i in 1:100) {
    # knn1 <- knn(train_CaseStudy2_raw[,c(1,18)],test_CaseStudy2_raw[,c(1,18)],train_CaseStudy2_raw$Attrition, k=i )
    knn1 <- knn(train_data[,3:Number_of_Cols],test_data[,3:Number_of_Cols],train_data$Attrition, k=i )#ERROR if data not normalized
    t_knn <- table(knn1, test_data$Attrition)
    CM_knn <- confusionMatrix(t_knn)
    #Capture Accuracy
    #ACC <- CM_knn$overall[1]
    Acc[seed,i] = CM_knn$overall[1]
    
  } 
}
#Caluclate mean accuracy for each of the seed/knn iteritions
mean_Acc = colMeans(Acc)
i_highest_acc <- which.max(mean_Acc)

#3. Run Knn and NB on the data set with different seed values
Conclusion_job_sat <- data.frame("Seed" = double() , "Accuracy_knn"  = double(), "Accuracy_NB" = double(),"Specificity_knn" = double() ,
                                 "Specificity_NB" = double(), "Sensitivity_knn"  = double()  , "Sensitivity_NB" = double() )

for (seed in 1:100)
{
  set.seed(seed)
  #Split the data set into train and test
  trainIndices = sample(seq(1:nrow(Base_Data)),round(.7*nrow(Base_Data)))
  train_data = Base_Data[trainIndices,]
  test_data = Base_Data[-trainIndices,] 
  
  #KNN
  knn1 <- knn(train_data[,3:Number_of_Cols],test_data[,3:Number_of_Cols],train_data$Attrition, k=i_highest_acc )#ERROR - TRY TO NORMALISE THE DATA
  t_knn <- table(knn1, test_data$Attrition)
  CM_knn <- confusionMatrix(t_knn)
  
  #NB
  model = naiveBayes(train_data[,3:Number_of_Cols], train_data$Attrition)
  NB_Predict <- predict(model,test_data[,3:Number_of_Cols])
  t_Predict <- table(NB_Predict,test_data$Attrition)
  CM_NB <- confusionMatrix(t_Predict)
  
  #Capture the comparision in a dataframe
  Conclusion <- data.frame( "Seed" = seed, "Accuracy_knn" = CM_knn$overall[1],"Accuracy_NB" = CM_NB$overall[1], 
                            "Specificity_knn" = CM_knn$byClass[2], "Specificity_NB" = CM_NB$byClass[2], 
                            "Sensitivity_knn" = CM_knn$byClass[1], "Sensitivity_NB" = CM_NB$byClass[1])
  #Merge the 2 dataframes
  Conclusion_job_sat <- rbind(Conclusion_job_sat,Conclusion) 
}

#Calculate Mean Accuracy, Specificity and Senitivity across all seeds for each model
mean_Accuracy_knn <- mean(Conclusion_job_sat$Accuracy_knn)
mean_Accuracy_NB <- mean(Conclusion_job_sat$Accuracy_NB)
mean_Specificity_knn <- mean(Conclusion_job_sat$Specificity_knn)
mean_Specificity_NB <- mean(Conclusion_job_sat$Specificity_NB)
mean_Sensitivity_knn <- mean(Conclusion_job_sat$Sensitivity_knn)
mean_Sensitivity_NB <- mean(Conclusion_job_sat$Sensitivity_NB)

#Putting all Means in one dataframe
Mean_Knn_NB <- data.frame( Test_Type = c("KNN", "NB"), Mean_Accuracy = c(mean_Accuracy_knn, mean_Accuracy_NB), 
                           Mean_Specificity=c(mean_Specificity_knn,mean_Specificity_NB ),
                           Mean_Sensitivity=c(mean_Sensitivity_knn, mean_Sensitivity_NB))

#print(paste("Modelling results for data set",Base_Data_Name) ) 
#Mean_Knn_NB$DAta_Set_Name <- Base_Data_Name
Mean_Knn_NB
#Capturing results for different data groups and different models
#Final_Model_Results <- rbind(Final_Model_Results,Mean_Knn_NB)
#Final_Model_Results

#NB Prediction: 
#Testing the provided file

colnames(CaseStudy2_Comp_set)
colnames(CaseStudy2_Comp_set) <- c("ID",	"Age","BusinessTravel",	"DailyRate",	"Department",	"DistanceFromHome",	"Education",	"EducationField",	"EmployeeCount",	"EmployeeNumber",	"EnvironmentSatisfaction",	"Gender",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole",	"JobSatisfaction",	"MaritalStatus",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18",	"OverTime",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager")
CaseStudy2_Comp_set$BusinessTravel_N <- ifelse(str_detect(CaseStudy2_Comp_set$BusinessTravel,'Non-Travel'),1, ifelse(str_detect(CaseStudy2_Comp_set$BusinessTravel,'Travel_Rarely'),2,ifelse(str_detect(CaseStudy2_Comp_set$BusinessTravel,'Travel_Frequently'),3,4)))
CaseStudy2_Comp_set$Gender_N <-ifelse(str_detect(CaseStudy2_Comp_set$Gender,"^Male"),1, ifelse(str_detect(CaseStudy2_Comp_set$Gender,"^Female"),2,3))
CaseStudy2_Comp_set$Over18_N <-ifelse(str_detect(CaseStudy2_Comp_set$Over18,"Y"),1, 2)
CaseStudy2_Comp_set$MaritalStatus_N <- ifelse(str_detect(CaseStudy2_Comp_set$MaritalStatus,'Single'),1, ifelse(str_detect(CaseStudy2_Comp_set$MaritalStatus,'Married'),2,ifelse(str_detect(CaseStudy2_Comp_set$MaritalStatus,'Divorced'),3,4)))
CaseStudy2_Comp_set$OverTime_N <-ifelse(str_detect(CaseStudy2_Comp_set$OverTime,"No"),1, ifelse(str_detect(CaseStudy2_Comp_set$OverTime,"Yes"),2,3))
CaseStudy2_Comp_set$Department_N <- ifelse(str_detect(CaseStudy2_Comp_set$Department,"Human Resources"),1, ifelse(str_detect(CaseStudy2_Comp_set$Department,"Research & Development"),2,3))
CaseStudy2_Comp_set$EducationField_N <- ifelse(str_detect(CaseStudy2_Comp_set$Department,"Human Resources"),1,ifelse(str_detect(CaseStudy2_Comp_set$Department,"Life Sciences"),2,
                                                                                                           ifelse(str_detect(CaseStudy2_Comp_set$Department,"Marketing"),3, 
                                                                                                                  ifelse(str_detect(CaseStudy2_Comp_set$Department, "Medical"),4,  
                                                                                                                         ifelse(str_detect(CaseStudy2_Comp_set$Department,"Other"),5, 6)))))     

CaseStudy2_Comp_set$JobRole_N <- ifelse(str_detect(CaseStudy2_Comp_set$JobRole,"Sales Executive"),1,ifelse(str_detect(CaseStudy2_Comp_set$Department,"Research Scientist"),2,
                                                                                                 ifelse(str_detect(CaseStudy2_Comp_set$Department,"Laboratory Technician"),3, 
                                                                                                        ifelse(str_detect(CaseStudy2_Comp_set$Department, "Manufacturing Director"),4,  
                                                                                                               ifelse(str_detect(CaseStudy2_Comp_set$Department,"Healthcare Representative"),5, 
                                                                                                                      ifelse(str_detect(CaseStudy2_Comp_set$Department,"Sales Representative"),6, 
                                                                                                                             7)))))   )  


#Exclude employee number and employee cnt from the data
CaseStudy2_comp_N <- CaseStudy2_Comp_set %>% select("ID",	"Age","BusinessTravel_N",	"DailyRate",	"Department_N",	"DistanceFromHome",	"Education",	"EducationField_N","EnvironmentSatisfaction",	"Gender_N",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole_N",	"JobSatisfaction",	"MaritalStatus_N",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18_N",	"OverTime_N",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager")

Number_of_Cols_1 <- ncol(CaseStudy2_comp_N)
Asnumber <- function(x) {return (as.numeric(x)) } # function convert measures to numberic
CaseStudy2_comp_N_nmbr <- as.data.frame(lapply(CaseStudy2_comp_N[,2:Number_of_Cols_1], Asnumber))
znorm_f <-function(x) {return (znorm(x)) } # function to Z-norm the data
Number_of_Cols_2 <- ncol(CaseStudy2_comp_N_nmbr)
znorm_CaseStudy2_comp_N_nmbr <- as.data.frame(lapply(CaseStudy2_comp_N_nmbr[,1:Number_of_Cols_2], znorm_f))
CaseStudy2_comp_N_Z <- cbind(CaseStudy2_comp_N[1],znorm_CaseStudy2_comp_N_nmbr) #combine z-norm data with ID and Attrition values
#head(CaseStudy2_N_Z)
Base_Data <- CaseStudy2_comp_N_Z
Number_of_Cols <- ncol(CaseStudy2_comp_N_Z)

NB_Predict_Att <- predict(model,CaseStudy2_comp_N_Z[,2:Number_of_Cols])
nrow(CaseStudy2_comp_N_Z)
answers <- cbind(NB_Predict_Att,CaseStudy2_comp_N_Z[1])
head(answers)
colnames(answers) <- c('Predcited Attrition','ID')
joined_data <- left_join(answers, CaseStudy2_Comp_set, by = "ID")
head(joined_data)
output <- select (joined_data,'Predcited Attrition',"ID",	"Age","BusinessTravel",	"DailyRate",	"Department",	"DistanceFromHome",	"Education",	"EducationField",	"EmployeeCount",	"EmployeeNumber",	"EnvironmentSatisfaction",	"Gender",	"HourlyRate",	"JobInvolvement",	"JobLevel",	"JobRole",	"JobSatisfaction",	"MaritalStatus",	"MonthlyIncome",	"MonthlyRate",	"NumCompaniesWorked",	"Over18",	"OverTime",	"PercentSalaryHike",	"PerformanceRating",	"RelationshipSatisfaction",	"StandardHours",	"StockOptionLevel",	"TotalWorkingYears",	"TrainingTimesLastYear",	"WorkLifeBalance",	"YearsAtCompany",	"YearsInCurrentRole",	"YearsSinceLastPromotion",	"YearsWithCurrManager") 
#PUT THE ANSWERS IN CSV

#Write output
write.csv(output, file = "C:/Users/simer/Documents/SMU/Doing_DataScience/Case_Study_2/Case2PredictionsClassifyREDDY.csv")

#EDA for Linear Regression


#EDA
M_p1 <- plot(CaseStudy2_N_Z[,c(3,5,8,12,14,15,18)])
M_p2 <- plot(CaseStudy2_N_Z[,c(18,19,20,22,23,24,26,28,31,32)])
plot(CaseStudy2_N_Z[,c(3, 5, 14, 18,28,31,32)])

#summary(CaseStudy2_raw)
#head(CaseStudy2_N_Z)
#Columns of interest : MonthlyIncome,JobLevel,Age,DailyRate,TotalWorkingYears,YearsAtCompany,YearsInCurrentRole
par(mfrow=c(3, 3)) 

#Scatter Plot of Shortlisted measures
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$JobLevel, main="JobLevel ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$Age, main="Age ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$DailyRate, main="DailyRate ~ MonthlyIncome") #pretty flat
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$TotalWorkingYears, main="TotalWorkingYears ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$YearsAtCompany, main="YearsAtCompany ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$YearsInCurrentRole, main="YearsInCurrentRole ~ MonthlyIncome")

#Extra measures
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$DistanceFromHome, main="DistanceFromHome ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$HourlyRate, main="HourlyRate ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$MonthlyRate, main="MonthlyRate ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$Education, main="Education ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$BusinessTravel, main="BusinessTravel ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$NumCompaniesWorked, main="NumCompaniesWorked ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$PerformanceRating, main="PerformanceRating ~ MonthlyIncome")
scatter.smooth(x=CaseStudy2_raw$MonthlyIncome, y=CaseStudy2_raw$YearsWithCurrManager, main="YearsWithCurrManager ~ MonthlyIncome")

# BOX PLOT to see outliers : Let's look at Job Level, Age, Total working years
par(mfrow=c(2, 2))  # divide graph area in 2 columns
boxplot(CaseStudy2_raw$MonthlyIncome, main="MonthlyIncome", sub=paste("Outlier rows: ", boxplot.stats(CaseStudy2_raw$MonthlyIncome)$out))  # box plot for 'speed'
boxplot(CaseStudy2_raw$Age, main="Age", sub=paste("Outlier rows: ", boxplot.stats(CaseStudy2_raw$Age)$out)) 
boxplot(CaseStudy2_raw$DailyRate, main="DailyRate", sub=paste("Outlier rows: ", boxplot.stats(CaseStudy2_raw$DailyRate)$out)) 
boxplot(CaseStudy2_raw$TotalWorkingYears, main="TotalWorkingYears", sub=paste("Outlier rows: ", boxplot.stats(CaseStudy2_raw$TotalWorkingYears)$out)) 
boxplot(CaseStudy2_raw$YearsAtCompany, main="YearsAtCompany", sub=paste("Outlier rows: ", boxplot.stats(CaseStudy2_raw$YearsAtCompany)$out)) 
boxplot(CaseStudy2_raw$YearsInCurrentRole, main="YearsInCurrentRole", sub=paste("Outlier rows: ", boxplot.stats(CaseStudy2_raw$YearsInCurrentRole)$out)) 
boxplot(CaseStudy2_raw$JobLevel, main="JobLevel", sub=paste("Outlier rows: ", boxplot.stats(CaseStudy2_raw$JobLevel)$out)) 

# Density Plot
par(mfrow=c(2, 2))  # divide graph area in 2 columns

plot(density(CaseStudy2_raw$MonthlyIncome), main="Density Plot: MonthlyIncome", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(CaseStudy2_raw$MonthlyIncome), 2)))  # density plot for 'MonthlyIncome'
polygon(density(CaseStudy2_raw$MonthlyIncome), col="red")

plot(density(CaseStudy2_raw$JobLevel), main="Density Plot: JobLevel", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(CaseStudy2_raw$JobLevel), 2)))  # density plot for 'MonthlyIncome'
polygon(density(CaseStudy2_raw$JobLevel), col="red")

plot(density(CaseStudy2_raw$Age), main="Density Plot: Age", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(CaseStudy2_raw$Age), 2)))  # density plot for 'Age'
polygon(density(CaseStudy2_raw$Age), col="red")

plot(density(CaseStudy2_raw$DailyRate), main="Density Plot: DailyRate", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(CaseStudy2_raw$DailyRate), 2)))  # density plot for 'DailyRate'
polygon(density(CaseStudy2_raw$DailyRate), col="red")

plot(density(CaseStudy2_raw$TotalWorkingYears), main="Density Plot: TotalWorkingYears", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(CaseStudy2_raw$TotalWorkingYears), 2)))   # density plot for 'TotalWorkingYears'
polygon(density(CaseStudy2_raw$TotalWorkingYears), col="red")

plot(density(CaseStudy2_raw$YearsAtCompany), main="Density Plot: YearsAtCompany", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(CaseStudy2_raw$YearsAtCompany), 2)))  # density plot for 'YearsAtCompany'
polygon(density(CaseStudy2_raw$YearsAtCompany), col="red")

plot(density(CaseStudy2_raw$YearsInCurrentRole), main="Density Plot: YearsInCurrentRole", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(CaseStudy2_raw$YearsInCurrentRole), 2)))  # density plot for 'CaseStudy2_raw$YearsInCurrentRole'
polygon(density(CaseStudy2_raw$YearsInCurrentRole), col="red")

#Correlation
cor(CaseStudy2_raw$MonthlyIncome, CaseStudy2_raw$JobLevel) #0.9517233
cor(CaseStudy2_raw$MonthlyIncome, CaseStudy2_raw$TotalWorkingYears) #0.7785329
cor(CaseStudy2_raw$MonthlyIncome, CaseStudy2_raw$Age) #0.4842501


#Let's start building lm with variable with highest correlation factor
#JOB LEVEL
linearMod_JL <- lm(MonthlyIncome ~ JobLevel, data=CaseStudy2_raw)  # build linear regression model on full data
print(linearMod_JL)
#MonthlyIncome = Intercept + (  JobLevel)
#MonthlyIncome = -1792 + 4014 * JobLevel
modelSummary_JL <- summary(linearMod_JL)
modelCoeffs_JL <- modelSummary_JL$coefficients
AIC_JL <- AIC(linearMod_JL)
BIC_JL <- BIC(linearMod_JL)
pred_MonthlyIncome <- predict(linearMod_JL, newdata = CaseStudy2_raw)
t_JL_Model_1 <- train(MonthlyIncome ~ JobLevel, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(t_JL_Model_1)
t_JL_Model_1$results #RMSE 1414.445/ r-sq 0.9053364

MonthlyIncome_preds = predict(linearMod_JL)
CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = JobLevel)) + geom_point() + geom_line(data = CaseStudy2_raw, aes( x = MonthlyIncome_preds, y = JobLevel, col = "red")) + ggtitle("LR Model: JobLevel vs MonthlyIncome") + scale_color_discrete(name = "Predicted")

linearMod_JL_sq <- lm(MonthlyIncome ~ JobLevel + I(JobLevel^2), data=CaseStudy2_raw)  #
linearMod_JL_sq_summary <- summary(linearMod_JL_sq)
linearMod_JL_sq_summary$coefficients

CaseStudy2_raw$JobLevelSQ <- CaseStudy2_raw$JobLevel^2
t_JL_Model_2 <- train(MonthlyIncome ~ JobLevel + JobLevelSQ, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(t_JL_Model_2)
CaseStudy2_raw <- CaseStudy2_raw %>% mutate(JobLevelSQ = JobLevel^2)
MonthlyIncome_preds2 = predict(t_JL_Model_2)
t_JL_Model_2$results # #RMSE  1436.79/ r-sq 0.9262231

#MODEL 1 IS BETTER
#t_JL_Model_3 <- train(MonthlyIncome ~ JobLevel + I(JobLevel^2) + I(JobLevel^3), method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
#t_JL_Model_3$results # #RMSE  1396.326
#summary(t_JL_Model_3)

#t_JL_Model_4 <- train(MonthlyIncome ~ JobLevel + I(JobLevel^2) + I(JobLevel^3) +   I(JobLevel^4), method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
#t_JL_Model_4$results # #RMSE  1378.202
#summary(t_JL_Model_4)

#t_JL_Model_5 <- train(MonthlyIncome ~ JobLevel + I(JobLevel^2) + I(JobLevel^3) +   I(JobLevel^4)  +   I(JobLevel^5), method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
#t_JL_Model_5$results #RMSE  1378.202
#summary(t_JL_Model_5)

#TotalWorkingYears
linearMod_T_Wrkng_Yrs_t <- train(MonthlyIncome ~ TotalWorkingYears , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_T_Wrkng_Yrs_t)
linearMod_T_Wrkng_Yrs_t$results #RmSE 2893.807 increased

CaseStudy2_raw <- CaseStudy2_raw %>% mutate(TotalWorkingYearsSQ = TotalWorkingYears^2)
linearMod_T_Wrkng_Yrs_t2 <- train(MonthlyIncome ~ TotalWorkingYears + TotalWorkingYearsSQ, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_T_Wrkng_Yrs_t2)
linearMod_T_Wrkng_Yrs_t2$results # rmsse 2896, never mind

t_JL_TWrkngHrs <- train(MonthlyIncome ~ JobLevel + TotalWorkingYears, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
t_JL_TWrkngHrs$results # RMSE 1392 BETTER THAN MODEL 1 JOB LEVEL
#T_Wrkng_Yrs_preds1 = predict(linearMod_T_Wrkng_Yrs_t)
#T_Wrkng_Yrs_preds2 = predict(linearMod_T_Wrkng_Yrs_t2)
#CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = TotalWorkingYears)) + geom_point() + geom_line(data = CaseStudy2_raw, aes( x = MonthlyIncome_preds, y = T_Wrkng_Yrs_preds1, col = "red")) + ggtitle("LR Model: JobLevel + Horsepower^2 + Horsepower^3 vs MPG") + scale_color_discrete(name = "Predicted")
#CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = TotalWorkingYears)) + geom_point() + geom_line(data = CaseStudy2_raw, aes( x = MonthlyIncome_preds, y = T_Wrkng_Yrs_preds2, col = "red")) + ggtitle("LR Model: JobLevel + Horsepower^2 + Horsepower^3 vs MPG") + scale_color_discrete(name = "Predicted")


linearMod_T_Wrkng_Yrs <- lm(MonthlyIncome ~ TotalWorkingYears, data=CaseStudy2_raw)  # build linear regression model on full data
#print(linearMod_T_Wrkng_Yrs)
#MonthlyIncome = Intercept + (  JobLevel)
#MonthlyIncome = -1902 + 4093 * JobLevel
modelSummary_T_Wrkng_Yrs <- summary(linearMod_T_Wrkng_Yrs)
modelCoeffs_T_Wrkng_Yrs <- modelSummary_T_Wrkng_Yrs$coefficients
AIC_T_Wrkng_Yrs <- AIC(linearMod_T_Wrkng_Yrs)
BIC_T_Wrkng_Yrs <- BIC(linearMod_T_Wrkng_Yrs)

T_Wrkng_Yrs_preds = predict(linearMod_T_Wrkng_Yrs)
#CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = TotalWorkingYears)) + geom_smooth() + geom_line(data = CaseStudy2_raw, aes( x = MonthlyIncome, y = T_Wrkng_Yrs_preds, col = "red")) + ggtitle("LR Model: Horsepower + Horsepower^2 + Horsepower^3 vs MPG") + scale_color_discrete(name = "Predicted")
#CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = JobLevel)) + geom_smooth() + geom_line(data = CaseStudy2_raw, aes( x = MonthlyIncome, y = T_Wrkng_Yrs_preds, col = "red")) + ggtitle("LR Model: Horsepower + Horsepower^2 + Horsepower^3 vs MPG") + scale_color_discrete(name = "Predicted")

#TotalWorkingYears
linearMod_Age <- lm(MonthlyIncome ~ Age, data=CaseStudy2_raw)  # build linear regression model on full data
print(linearMod_Age)

linearMod_Age_JL <- lm(MonthlyIncome ~ Age + JobLevel, data=CaseStudy2_raw)  # build linear regression model on full data
print(linearMod_Age_JL)
AIC(linearMod_Age_JL)
BIC(linearMod_Age_JL)

linearMod_Age_JL_TWH <- lm(MonthlyIncome ~ Age + JobLevel + TotalWorkingYears, data=CaseStudy2_raw)  # build linear regression model on full data
print(linearMod_Age_JL_TWH)
AIC(linearMod_Age_JL_TWH)
BIC(linearMod_Age_JL_TWH)

linearMod_Age_t <- train(MonthlyIncome ~ Age , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_Age_t)
linearMod_Age_t$results #RmSE 4033.305

#MonthlyIncome = Intercept + (  JobLevel)
#MonthlyIncome = -1902 + 4093 * JobLevel
modelSummary_Age <- summary(linearMod_Age)
modelCoeffs_Age <- modelSummary_Age$coefficients
AIC_Age <- AIC(linearMod_Age)
BIC_Age <- BIC(linearMod_Age)

AIC_BIC_LM_JL <- data.frame("Measure" = c("AIC","BIC"), "lm_on" = c("JobLevel","JobLevel"), "Value" = c(AIC_JL,BIC_JL))
AIC_BIC_LM_T_Wrkng_Yrs <- data.frame("Measure" = c("AIC","BIC"), "lm_on" = c("TotalWorkingYears","TotalWorkingYears"), "Value" = c(AIC_T_Wrkng_Yrs,BIC_T_Wrkng_Yrs))
AIC_BIC_LM_Age <- data.frame("Measure" = c("AIC","BIC"), "lm_on" = c("Age","Age"), "Value" = c(AIC_Age,BIC_Age))
AIC_BIC <- rbind(AIC_BIC_LM_JL,AIC_BIC_LM_T_Wrkng_Yrs,AIC_BIC_LM_Age)
AIC(linearMod_Age_JL)
BIC(linearMod_Age_JL)
AIC(linearMod_Age_JL_TWH)
BIC(linearMod_Age_JL_TWH)
AIC_BIC

linearMod_Age_T_Wrkng_Yrs_jl <- train(MonthlyIncome ~ Age + TotalWorkingYears + JobLevel  , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_Age_T_Wrkng_Yrs_jl)
linearMod_Age_T_Wrkng_Yrs_jl$results #RMSE 1393

t_JL_TWrkngHrs <- train(MonthlyIncome ~ JobLevel + TotalWorkingYears, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
t_JL_TWrkngHrs$results # RMSE 1392.143

#COMBINING ALL 3 MEASURES
linearMod_Age_JL_TWH <- lm(MonthlyIncome ~ Age + JobLevel + TotalWorkingYears, data=CaseStudy2_raw)  # build linear regression model on full data
print(linearMod_Age_JL_TWH)
AIC(linearMod_Age_JL_TWH)
BIC(linearMod_Age_JL_TWH)

CaseStudy2_raw$JobLevelCub <- CaseStudy2_raw$JobLevel^3
CaseStudy2_raw$JobLevelCub <- CaseStudy2_raw$JobLevel^3

linearMod_Age_T_Wrkng_Yrs_jl2 <- train(MonthlyIncome ~ Age + TotalWorkingYears + JobLevel + JobLevelCub , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_Age_T_Wrkng_Yrs_jl)
linearMod_Age_T_Wrkng_Yrs_jl$results #RMSE 1303
#Predict_JL_Age_Model_1 <- predict(JL_Age_Model_1)
Sum_ge_T_Wrkng_Yrs_jl <- summary(linearMod_Age_T_Wrkng_Yrs_jl)
Sum_ge_T_Wrkng_Yrs_jl$r.squared #r-sq 0.92


MonthlyIncome_preds = predict(linearMod_JL)
CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = JobLevel)) + geom_point() + geom_line(data = CaseStudy2_raw, aes( x = MonthlyIncome_preds, y = JobLevel, col = "red")) + ggtitle("LR Model: JobLevel vs MonthlyIncome") + scale_color_discrete(name = "Predicted")

MonthlyIncome_preds2 = predict(t_JL_Model_2)
CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = JobLevel)) + geom_point() + geom_line(data = CaseStudy2_raw, aes( x = MonthlyIncome_preds2, y = JobLevel, col = "red")) + ggtitle("LR Model: JobLevel + JobLevel^2  vs MonthlyIncome") + scale_color_discrete(name = "Predicted")


CaseStudy2_raw$TotalWorkingYearsSQ <- CaseStudy2_raw$TotalWorkingYears^2
TWH_Model_2 <- train(MonthlyIncome ~ TotalWorkingYears + TotalWorkingYearsSQ, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_TWH_Model_2 <- predict(TWH_Model_2)
CaseStudy2_raw %>% ggplot(aes(x = TotalWorkingYears, y = Predict_TWH_Model_2)) + geom_smooth() + geom_point()

CaseStudy2_raw$TotalWorkingYearsCub <- CaseStudy2_raw$TotalWorkingYears^3
TWH_Model_3 <- train(MonthlyIncome ~ TotalWorkingYears + TotalWorkingYearsSQ + TotalWorkingYearsCub, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_JL_Model_3 <- predict(TWH_Model_3)
CaseStudy2_raw %>% ggplot(aes(x = TotalWorkingYears, y = Predict_JL_Model_3)) + geom_smooth() + geom_point()


CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = Age)) + geom_smooth()

Age_Model_1 <- train(MonthlyIncome ~ Age, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_Age_Model_1 <- predict(Age_Model_1)
#CaseStudy2_raw %>% ggplot(aes(x = Predict_TWH_Model_1, y = TotalWorkingYears)) + geom_smooth() + geom_point()
CaseStudy2_raw %>% ggplot(aes(x = Age, y = Predict_Age_Model_1)) + geom_smooth() + geom_point()


CaseStudy2_raw$TotalWorkingYearsSQ <- CaseStudy2_raw$TotalWorkingYears^2
TWH_Model_2 <- train(MonthlyIncome ~ TotalWorkingYears + TotalWorkingYearsSQ, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_TWH_Model_2 <- predict(TWH_Model_2)
CaseStudy2_raw %>% ggplot(aes(x = TotalWorkingYears, y = Predict_TWH_Model_2)) + geom_smooth() + geom_point()

CaseStudy2_raw$TotalWorkingYearsCub <- CaseStudy2_raw$TotalWorkingYears^3
TWH_Model_3 <- train(MonthlyIncome ~ TotalWorkingYears + TotalWorkingYearsSQ + TotalWorkingYearsCub, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_JL_Model_3 <- predict(TWH_Model_3)
CaseStudy2_raw %>% ggplot(aes(x = TotalWorkingYears, y = Predict_JL_Model_3)) + geom_smooth() + geom_point()



summary(t_JL_Model_2)
CaseStudy2_raw <- CaseStudy2_raw %>% mutate(JobLevelSQ = JobLevel^2)
MonthlyIncome_preds2 = predict(t_JL_Model_2)

Predict_JL_1 <- predict(t_JL_Model_1)
CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = JobLevel)) + geom_smooth()
#CaseStudy2_raw %>% ggplot(aes(x = Final_Predict, y = JobLevel)) + geom_smooth()
CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome_preds2, y = JobLevel)) + geom_smooth()

#More EDA
CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = JobLevel)) + geom_smooth()

JL_Model_1 <- train(MonthlyIncome ~ JobLevel, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_JL_Model_1 <- predict(JL_Model_1)
Sum_JL_Model_1 <-summary(JL_Model_1)
CaseStudy2_raw %>% ggplot(aes(x = Predict_JL_Model_1, y = JobLevel)) + geom_smooth() + geom_point()
CaseStudy2_raw %>% ggplot(aes(x = JobLevel, y = Predict_JL_Model_1)) + geom_smooth() + geom_point()


CaseStudy2_raw$JobLevelSQ <- CaseStudy2_raw$JobLevel^2
JL_Model_2 <- train(MonthlyIncome ~ JobLevel + JobLevelSQ, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_JL_Model_2 <- predict(JL_Model_2)
Sum_JL_Model_2 <-summary(JL_Model_2)
CaseStudy2_raw %>% ggplot(aes(x = JobLevel, y = Predict_JL_Model_2)) + geom_smooth() + geom_point()

CaseStudy2_raw$JobLevelCub <- CaseStudy2_raw$JobLevel^3
JL_Model_3 <- train(MonthlyIncome ~ JobLevel + JobLevelSQ + JobLevelCub, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_JL_Model_3 <- predict(JL_Model_3)
Sum_JL_Model_3 <- summary(JL_Model_3)
CaseStudy2_raw %>% ggplot(aes(x = JobLevel, y = Predict_JL_Model_3)) + geom_smooth()


CaseStudy2_raw %>% ggplot(aes(x = MonthlyIncome, y = TotalWorkingYears)) + geom_smooth()

TWY_Model_1 <- train(MonthlyIncome ~ TotalWorkingYears, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_TWY_Model_1 <- predict(TWY_Model_1)
Sum_TWY_Model_1 <- summary(TWY_Model_1)

CaseStudy2_raw$TotalWorkingYearsSQ <- CaseStudy2_raw$TotalWorkingYears^2
TWY_Model_2 <- train(MonthlyIncome ~ TotalWorkingYears + TotalWorkingYearsSQ , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_TWY_Model_2 <- predict(TWY_Model_2)
Sum_TWY_Model_2 <- summary(TWY_Model_2)
#CaseStudy2_raw %>% ggplot(aes(x = Predict_TWH_Model_1, y = TotalWorkingYears)) + geom_smooth() + geom_point()
#CaseStudy2_raw %>% ggplot(aes(x = TotalWorkingYears, y = Predict_TWH_Model_1)) + geom_smooth() + geom_point()

JL_TWH_Model_1 <- train(MonthlyIncome ~ JobLevel + TotalWorkingYears, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_JL_TWH_Model_1 <- predict(JL_TWH_Model_1)
Sum_JL_TWH_Model_1 <- summary(JL_TWH_Model_1)

TWH_JL_Model_1 <- train(MonthlyIncome ~ TotalWorkingYears +JobLevel , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_TWH_JL_Model_1 <- predict(TWH_JL_Model_1)
Sum_TWH_JL_Model_1 <- summary(TWH_JL_Model_1)

Age_Model_1 <- train(MonthlyIncome ~ Age, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_Age_Model_1<- predict(Age_Model_1)
Sum_Age_Model_1 <- summary(Age_Model_1)

CaseStudy2_raw$AgeSQ <- CaseStudy2_raw$Age^2
Age_Model_2 <- train(MonthlyIncome ~ Age + AgeSQ , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_Age_Model_2 <- predict(Age_Model_2)
Sum_Age_Model_2 <- summary(Age_Model_2)

TWH_Age_Model_1 <- train(MonthlyIncome ~ Age + TotalWorkingYears , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_TWH_Age_Model_1 <- predict(TWH_Age_Model_1)
Sum_TWH_Age_Model_1 <- summary(TWH_Age_Model_1)

JL_Age_Model_1 <- train(MonthlyIncome ~ Age + JobLevel , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_JL_Age_Model_1 <- predict(JL_Age_Model_1)
Sum_JL_Age_Model_1 <- summary(JL_Age_Model_1)

Sum_JL_Age_Model_1$r.squared #0.9141776
Sum_TWH_Age_Model_1$r.squared #0.616751
Sum_Age_Model_2$r.squared #0.2755832
Sum_Age_Model_1$r.squared #0.2755832
Sum_JL_TWH_Model_1$r.squared #0.915356
Sum_JL_TWH_Model_1$r.squared #0.915356
Sum_JL_Model_1$r.squared #0.9141695
Sum_JL_Model_2$r.squared #0.9274724
Sum_JL_Model_3$r.squared # 0.9320185
Sum_TWY_Model_1$r.squared # 0.6122029
Sum_TWY_Model_2$r.squared #0.6156517

#Predict_Age_Model_1
Age_Model_1 <- train(MonthlyIncome ~ Age, method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
Predict_Age_Model_1<- predict(Age_Model_1)
Sum_Age_Model_1 <- summary(Age_Model_1)
CaseStudy2_raw %>% ggplot(aes(x = Age, y = MonthlyIncome)) + geom_smooth() + geom_point()
CaseStudy2_raw %>% ggplot(aes(x = Age, y = Predict_Age_Model_1)) + geom_smooth() + geom_point()

CaseStudy2_raw_Under_50 <- CaseStudy2_raw %>% filter(Age <=53)
CaseStudy2_raw_Over_50 <- CaseStudy2_raw %>% filter(Age >53)
nrow(CaseStudy2_raw_Under_50)
nrow(CaseStudy2_raw_Over_50)


linearMod_Age_T_Wrkng_Yrs_jl2 <- train(MonthlyIncome ~ Age + TotalWorkingYears + JobLevel + JobLevelCub , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_Age_T_Wrkng_Yrs_jl2)
linearMod_Age_T_Wrkng_Yrs_jl2$results #RMSE 1303
Predict_Age_T_Wrkng_Yrs_jl2 <- predict(linearMod_Age_T_Wrkng_Yrs_jl2)
Sum_Age_T_Wrkng_Yrs_jl2 <- summary(linearMod_Age_T_Wrkng_Yrs_jl2)
Sum_Age_T_Wrkng_Yrs_jl2$r.squared #r-sq 0.92
CaseStudy2_raw %>% ggplot(aes(x = TotalWorkingYears, y = Predict_Age_T_Wrkng_Yrs_jl2)) + geom_smooth() + geom_point()

linearMod_Age_T_Wrkng_Yrs_jl2 <- train(MonthlyIncome ~ Age + TotalWorkingYears + JobLevel + JobLevelCub , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_Age_T_Wrkng_Yrs_jl2)
linearMod_Age_T_Wrkng_Yrs_jl2$results #RMSE 1303
Predict_Age_T_Wrkng_Yrs_jl2 <- predict(linearMod_Age_T_Wrkng_Yrs_jl2)
Sum_Age_T_Wrkng_Yrs_jl2 <- summary(linearMod_Age_T_Wrkng_Yrs_jl2)
Sum_Age_T_Wrkng_Yrs_jl2$r.squared #r-sq 0.92
CaseStudy2_raw %>% ggplot(aes(x = Age, y = Predict_Age_T_Wrkng_Yrs_jl2)) + geom_smooth() + geom_point()

LM_Under_50 <- train(MonthlyIncome ~ Age + TotalWorkingYears + JobLevel + JobLevelCub , method = "lm", data = CaseStudy2_raw_Under_50, trControl = trainControl(method = "LOOCV"))
summary(LM_Under_50)
LM_Under_50$results #RMSE 1300
Predict_LM_Under_50 <- predict(LM_Under_50)
Sum_LM_Under_50 <- summary(LM_Under_50)
Sum_LM_Under_50$r.squared #r-sq 0.908
CaseStudy2_raw_Under_50 %>% ggplot(aes(x = Age, y = Predict_LM_Under_50)) + geom_smooth() + geom_point()

LM_Over_50 <- train(MonthlyIncome ~ Age + TotalWorkingYears + JobLevel  , method = "lm", data = CaseStudy2_raw_Over_50, trControl = trainControl(method = "LOOCV"))
summary(LM_Over_50)
LM_Over_50$results #RMSE 1300
Predict_LM_Over_50 <- predict(LM_Over_50)
Sum_LM_Over_50 <- summary(LM_Over_50)
Sum_LM_Over_50$r.squared #r-sq 0.908
CaseStudy2_raw_Over_50 %>% ggplot(aes(x = Age, y = Predict_LM_Over_50)) + geom_smooth() + geom_point()
#Final SALARY MODEL
CaseStudy2_raw$JobLevelCub <- CaseStudy2_raw$JobLevel^3
linearMod_Age_T_Wrkng_Yrs_jl2 <- train(MonthlyIncome ~ Age + TotalWorkingYears + JobLevel + JobLevelCub , method = "lm", data = CaseStudy2_raw, trControl = trainControl(method = "LOOCV"))
summary(linearMod_Age_T_Wrkng_Yrs_jl2)
linearMod_Age_T_Wrkng_Yrs_jl2$results #RMSE 1303
Predict_Age_T_Wrkng_Yrs_jl2 <- predict(linearMod_Age_T_Wrkng_Yrs_jl2)
Sum_Age_T_Wrkng_Yrs_jl2 <- summary(linearMod_Age_T_Wrkng_Yrs_jl2)
Sum_Age_T_Wrkng_Yrs_jl2$r.squared #r-sq 0.92
#CaseStudy2_raw %>% ggplot(aes(x = Age, y = Predict_Age_T_Wrkng_Yrs_jl2)) + geom_smooth() + geom_point() + ylab("Predicted Salary") +ggtitle("Plot showing the predicted salary vs.Age")

#CaseStudy2_Comp_Sal_set<- read.csv(file.choose(), header = TRUE, sep=',')
colnames(CaseStudy2_Comp_Sal_set)
colnames(CaseStudy2_Comp_Sal_set) <-c("ID","Age","Attrition","BusinessTravel","DailyRate","Department","DistanceFromHome","Education","EducationField","EmployeeCount", "EmployeeNumber", "EnvironmentSatisfaction","Gender","HourlyRate","JobInvolvement","JobLevel","JobRole","JobSatisfaction", "MaritalStatus","MonthlyRate", "NumCompaniesWorked","Over18","OverTime","PercentSalaryHike","PerformanceRating","RelationshipSatisfaction","StandardHours","StockOptionLevel","TotalWorkingYears","TrainingTimesLastYear",                          "WorkLifeBalance","YearsAtCompany","YearsInCurrentRole","YearsSinceLastPromotion", "YearsWithCurrManager")

CaseStudy2_Comp_Sal_set$JobLevelCub <- CaseStudy2_Comp_Sal_set$JobLevel^3
Predict_Comp_Sal_set <- round(predict(linearMod_Age_T_Wrkng_Yrs_jl2, newdata = CaseStudy2_Comp_Sal_set),0)

answers_sal <- cbind(Predict_Comp_Sal_set,CaseStudy2_Comp_Sal_set[1])
head(answers_sal)
colnames(answers_sal) <- c('Predicted Salary','ID')
joined_data_sal <- left_join(answers_sal, CaseStudy2_Comp_Sal_set, by = "ID")
head(joined_data_sal)
output_sal <- select (joined_data_sal,"Predicted Salary", "ID","Age","Attrition","BusinessTravel","DailyRate","Department","DistanceFromHome","Education","EducationField","EmployeeCount",              "EmployeeNumber","EnvironmentSatisfaction", "Gender","HourlyRate","JobInvolvement","JobLevel","JobRole","JobSatisfaction","MaritalStatus","MonthlyRate","NumCompaniesWorked","Over18","OverTime","PercentSalaryHike","PerformanceRating","RelationshipSatisfaction","StandardHours","StockOptionLevel","TotalWorkingYears","TrainingTimesLastYear","WorkLifeBalance","YearsAtCompany","YearsInCurrentRole","YearsSinceLastPromotion","YearsWithCurrManager")

write.csv(output_sal, file = "C:/Users/simer/Documents/SMU/Doing_DataScience/Case_Study_2/Case2PredictionsRegressREDDY.csv")




```




